Research

### 2025-09-29 research.qmd
talks
Font update
research profile update

-   Topics: Public policy evaluation on health IT, Digital technologies, Economics of AI
-   Methodologies: Causal inference with econometrics, machine learning, statistical learning

@@

1. **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) -- *Under Review at Information Systems Research*

@@

### Public policy Evaluation on Health IT

@@

2. **Pro-Choice Vs Pro-Life: The Impact of Telehealth Abortion on Infant Health.** -- *Data collected, working on empirical analysis*

## Presentations

>>>>

-   **Topics:** Public policy evaluation on health IT, Digital technologies, Artificial intelligence (AI) for Behavioral Decision-making, Economics of AI
-   **Methodologies:** Applied econometrics, experiments, machine learning, statistical learning

@@

1.  **Smartphone Use, Social Support, and Sleep Health.** Shaokang Yang, Idris Adjerid. [SSRN](http://dx.doi.org/10.2139/ssrn.5368531) -- *Under Review at **Information Systems Research***

@@

### Public Policy Evaluation on Health IT

@@

2.  **Pro-Choice Vs Pro-Life: The Impact of Healthcare Digitalization on Infant Health.** -- *Data collected, working on empirical analysis*

### AI for Behavioral Decision-making

1.  **Prevention is Better Than Cure: Artificial Intelligence-based Nudging to Prevent Digital Addiction.** -- *Ideation phase.*

## Talks
